---
title: "Regression Report"
author: #"`r #paramJson$UserFullName`"
date: #"`r #Sys.Date()`"
output:
html_document: default
pdf_document: default
---

```{r set-options, eval = TRUE, echo = FALSE, include = FALSE}
options(width = 150)
library(magrittr)
library(knitr)
library(kableExtra)
library(jsonlite)
library(jtools)
library(tidyverse)
library(broom)
library(data.table)
library(gridExtra)
library(ggthemes)
library(ggpubr)
library(GGally)
library(plotly)
library(grid)
library(olsrr)
library(fBasics)
library(car)
library(lmSubsets)
library(rmarkdown)
```

## Estimated Equation
```{r eval = TRUE, echo = FALSE}
    EstimatedEquation
```

***
## Descriptive Statistics
```{r eval = TRUE, echo = FALSE, results="asis"}
    DescriptiveStatistics
```

***
## Run Summary Report
```{r eval = TRUE, echo = FALSE, dpi=250}
    RunSummaryReport
```

***
## Correlation Matrix
```{r eval = TRUE, echo = FALSE, dpi=150}
    CorrelationMatrix
```

***
## Coefficients T-Tests and Confidence Intervals
```{r eval = TRUE, echo = FALSE, dpi=250}
    Coefficient
```                  

***
## Analysis of Variance Detail (ANOVA)
```{r eval = TRUE, echo = FALSE, dpi=250}
    ANOVATable
```

***
## R-Squared Report
```{r eval = TRUE, echo = FALSE, dpi=250}
    RSqReport
```

***
## Variable Omission Report
```{r eval = TRUE, echo = FALSE, dpi=250}
    if (IndepVariableCount > 2) {
      VarOmissionFull
    }
```    

***
## Multicollinearity Table
```{r eval = TRUE, echo = FALSE, dpi=250}
    MulticollinearityTable
```                  

***
## Histogram and QQ-Plots
```{r eval = TRUE, echo = FALSE, dpi=150}
    HistResidual
    QQPlotly
``` 

***
## Normality Output
```{r eval = TRUE, echo = FALSE, dpi=250}                       
    NormalityOutput
```

***
## Residual of Y vs Predicted Y
```{r eval = TRUE, echo = FALSE, dpi=150}                  
    YvPredY
```

***
## Residual of Y vs Sale Price
```{r eval = TRUE, echo = FALSE, dpi=150}
    ResYvSP
```                  

***
## Fitted Y vs Fitted X Plots
```{r eval = TRUE, echo = FALSE, dpi=150}
    FittedPlots
```

***
## Component + Residual Plots
```{r eval = TRUE, echo = FALSE, dpi=150}
    CompResidPlots
```